SVG: The Paper

### 2022-06-09 Analysis/index.Rmd
new graph for init sel

create_post_plot("x") + create_post_plot("y") 
ggsave("../Figures/init_sel_mdl.pdf", width = 10, height = 3.5)
```

>>>>

am %>% mutate(mu = a/(a+b)) %>%
  pivot_wider(observer, names_from = "dim", values_from = "mu") %>%
  ggplot(aes(x, y)) + geom_point(alpha = 0.5) +
  scale_x_continuous("mean x") + 
  scale_y_continuous("mean y") -> plt_mu

create_post_plot("x") + create_post_plot("y") + plt_mu
ggsave("../Figures/init_sel_mdl.pdf", width = 10, height = 3.5)
```
